Mixture Models for Single-Cell Assays with Application to Vaccine Studies: Supplementary Materials

### 2013-05-24 SupplementaryMaterialMIMOSA.tex
More revisions
update paper

%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%%   \includegraphics[width=.75\columnwidth]{Figures/2}\\
%%   \includegraphics[width=.75\columnwidth]{Figures/12}
%\begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0){\includegraphics[width=.5\columnwidth]{Figures/14}};
%    \node[anchor=south west, inner sep=0] at (8,0){\includegraphics[width=.5\columnwidth]{Figures/15}};
%    \node[anchor=south west, inner sep=0] at (0,-3.75){\includegraphics[width=.5\columnwidth]{Figures/16}};
%
%
%    \node at (0,3.4) [font=\small\sffamily] {A} ;
%    \node at (8,3.4) [font=\small\sffamily] {B} ;
%    \node at (0,-0.5) [font=\small\sffamily] {C} ;
%    \end{tikzpicture}
%   \caption{Comparison of MIMOSA on other cytokines and cytokine combinations for ENV-1-PTEG and GAG-1-PTEG stimulated CD4+ T-cells from the HVTN065 trial.}
%\label{fig:HVTN065ResultsCont}
%\end{figure}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_50K.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_50K.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_10K.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_10K.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model
     violating model assumptions and to two-sided data with small
     counts. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution.  A) The average ROC from 10 simulation
     with N=50,000 events. B) The average observed and nominal FDR from
     10 simulations with N=50,000 events. C) Average ROC for N=10,000
     events D) Average observed and nominal FDR for N=10,000 events.
}
   \label{webfig:simulations_trunc}
\end{figure}
\clearpage

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.75	\columnwidth]{Figures/Sim_OneSided_ROC_varyNobs.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.75\columnwidth]{Figures/Sim_OneSided_FDR_varyNobs.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \end{tikzpicture}
   \caption{One--sided MIMOSA model fit to simulated data with 50K events and varying values of I (number of observations). A) Average ROC curves from 10 simulations for 20, 50 and 100 observations. B) Average observed and nominal FDR from 10 simulations for 20, 50, and 100 observations. This figure appears in color in the electronic version of this article.
}
   \label{webfig:simulations_Nobs}
\end{figure}
\clearpage
\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.75	\columnwidth]{Figures/competeROC.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.75\columnwidth]{Figures/competeROCfdr.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \end{tikzpicture}
   \caption{Effect of deviations of the assumptions of 100\% true responders at the post-vaccine time point on A) ROC and B) FDR curves. The true response rate is shown in the gray box above each plot.
}
   \label{webfig:simulations_Nobs}
\end{figure}
\clearpage

>>>>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.75	\columnwidth]{Figures/competeROC.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.75\columnwidth]{Figures/competeROCfdr.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \end{tikzpicture}
   \caption{Effect of deviations of the assumptions of 100\% true responders at the post-vaccine time point on A) ROC and B) FDR curves. The true response rate is shown in the gray box above each plot.
}
   \label{webfig:simulations_competeroc}
\end{figure}
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%%   \includegraphics[width=.75\columnwidth]{Figures/2}\\
%%   \includegraphics[width=.75\columnwidth]{Figures/12}
%\begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0){\includegraphics[width=.5\columnwidth]{Figures/14}};
%    \node[anchor=south west, inner sep=0] at (8,0){\includegraphics[width=.5\columnwidth]{Figures/15}};
%    \node[anchor=south west, inner sep=0] at (0,-3.75){\includegraphics[width=.5\columnwidth]{Figures/16}};
%
%
%    \node at (0,3.4) [font=\small\sffamily] {A} ;
%    \node at (8,3.4) [font=\small\sffamily] {B} ;
%    \node at (0,-0.5) [font=\small\sffamily] {C} ;
%    \end{tikzpicture}
%   \caption{Comparison of MIMOSA on other cytokines and cytokine combinations for ENV-1-PTEG and GAG-1-PTEG stimulated CD4+ T-cells from the HVTN065 trial.}
%\label{fig:HVTN065ResultsCont}
%\end{figure}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.75	\columnwidth]{Figures/Sim_OneSided_ROC_varyNobs.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.75\columnwidth]{Figures/Sim_OneSided_FDR_varyNobs.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \end{tikzpicture}
   \caption{One--sided MIMOSA model fit to simulated data with 50K cells and varying values of I (number of observations). A) Average ROC curves from 10 simulations for 20, 50 and 100 observations. B) Average observed and nominal FDR from 10 simulations for 20, 50, and 100 observations. This figure appears in color in the electronic version of this article.
}
   \label{webfig:simulations_Nobs}
\end{figure}
\clearpage

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_10K.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_10K.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_50K.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_50K.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to two-sided data with small
     counts  and to  data from a model
     violating model assumptions.  For two-sided data A) the average ROC from 10 simulation
     with N=10,000 cells. B) the average observed and nominal FDR from
     10 simulations with N=10,000 cells. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution. C) Average ROC for N=50,000
     cells D) Average observed and nominal FDR for N=50,000 cells.
}
   \label{webfig:simulations_trunc}
\end{figure}
\clearpage
